Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-10 paper/main.tex
writing up some quick notes for results section (backing up progress)

>>>>

- what do additonal visual features add?  (compare reduced vs. feature rich)
- are the visual features "sticky"?  (compare feature rich vs. reduced (early), also reduced vs. reduced (early))
- are impoverished stimuli "sticky"?  (compare feature rich vs. reduced (late), reduced vs. reduced (late), also reduced (early) vs. reduced (late))

- are order effects "sticky"?  compare behavior on early vs. late lists for order manipulation condition
  - does feature clustering on early lists correlate with recall on early (or late) lists?
  - does feature clustering on late lists correlate with recall on early (or late) lists?
  - (ditto, but replace "recall" with "temporal clustering")

- for feature-rich lists, do order effects matter?
  - recall + dynamics + organization on order-manipulation conditions vs. feature rich
  - fingerprint trajectories: how much do fingerprints change over time, are they sensitive to order manipulations?

- are fingerprints maleable?  how does match between fingerprint + presentation order affect recall performance (adaptive conditions)?
